Figures

### 2019-11-27 figures/07_model-selection.Rmd
precompute simplified hu4s

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
# setwd("figures")
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal", quiet = TRUE)
hu4_all       <- st_crop(hu4_all, st_transform(study_bbox, st_crs(hu4_all)))

>>>>

```{r tn_re_hu4, fig.width = 3.77, fig.height = 4.5}
# setwd("figures")
study_bbox    <- st_read("../data/gis.gpkg", "study_bbox", quiet = TRUE)[3,]
states_all    <- st_read("../data/gis.gpkg", "states_all", quiet = TRUE)
hu4_all       <- st_read("../data/gis.gpkg", "hu4s_focal_simple", quiet = TRUE)
